Continuously Generalizing Buildings to Built-up Areas\\ by Aggregating and Growing

### 2017-10-17 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added section of running time; improved abstract and introduction

A way to achieve continuous generalization is to use morphing.
Often, a start map and a goal map, 
respectively at a larger scale and a smaller scale, 
are used as input, 
then maps at intermediate scales are produced 
while the start map is morphed to the goal map.
In order to morph, correspondences between two maps need to be defined.
For example, corresponding points between a pair of polylines have been 
investigated based on 
dynamic programming \citep{Noellenburg2008}, 
Delaunay triangulations and binary line generalized tree (BLG-tree)  
\citep{Deng2015},
and simulated annealing \citep{Li2017_Annealing}.
From a point to its corresponding point,
a straight-line trajectory is often used to interpolate.
Using morphing, \citet{Peng2016_Admin} continuously generalized 
administrative boundaries based on compatible triangulations. When the number 
of line features is different in the start and goal maps, a continuous 
selection is required and \citet{Chimani2014_Eat} proposed to generate a 
selection sequence applicable for road network.
They removed one road at each step while keeping the remaining roads connected.

These methods are interesting but only work on lines and our problem of 
building polygon interpolation cannot be achieved by similar morphings. 
Regarding the continuous generalization of polygon map features,
\citet{Danciger2009} proposed to grow polygons when a map was zoomed out. Their 
method 
preserves polygons' topology, area-ratios, and relative positions.  In the case 
where the goal map is an aggregated version of start land-cover map, 
\citet{Peng2017_AStar} computed optimal aggregation sequences for land-cover 
areas.

Buildings are important elements on maps, many methods have been proposed to 
generalize them but not necessarily in a continuous way.
For example, \citet{haunertwolff2010} simplified a set of buildings 
based an integer program.
Their simplification minimizes the number of edges of all the buildings 
and guarantees that the errors are smaller than a user-defined tolerance.
At the same time, no topological conflict is introduced by the simplification.
\citet{Buchin2011_Simp} simplified buildings based on an edge-move operation.
One advantage is that their method preserves orientations of the edges.

When users zoom out on digital maps, 
buildings become smaller and the distances between buildings decrease. So 
simplification is not the only necessary operation, and buildings can also be 
aggregated to legible enough \cite{Weibel1997}. Several methods were proposed 
to aggregate buildings while preserving the shape of buildings (right angles 
remain) \cite{Regnauld2001}, \cite{RegnauldRevell07}, \cite{Damen2008}. These 
algorithms can be used as inspirations to define a continuous transformation of 
buildings.

@@

Finally, some papers directly tackle the continuous transformation of buildings 
when scale is reduced. \citet{Li2017_Building} morphed between two buildings at 
different scales.
They managed to preserve the orthogonal characteristics of buildings, but their 
algorithm cannot be used in our case as the goal map does not contain buildings 
anymore. \citet{Touya17b} proposed a progressive transformation of buildings 
into a built-up area, where buildings are progressively replaced by the shape 
of the block they belong to. However, this last algorithm is not continuous 
enough, as each iteration directly transforms a set of buildings in a block 
into a polygon that covers the whole block. So there is no existing solution 
for the continuous generalization of building polygons into built-up area 
polygons.

@@

Our way of detecting close buildings is simple.
We buffer buildings with distance $d_{\epsilon, t}/2$ using round joins
(see \fig\ref{fig:Buffer_ThreeKinds}b).
We merge the buffers that overlap each other.
The buildings intersect the same merged buffer 
are identified as a group of close buildings.
The corresponding original buildings 
are identified as a group of original close buildings.
For each pair of the original buildings in the same group,
we connect them by adding a line segment linking the nearest points.
The line segments for a group of original buildings may cross each other or 
even intersect buildings.
To make the topology simple, 
we only select some of the line segments as \emph{bridges}.  
We consider each building as a node and each line segment as an edge, 
then we have a graph.
Using Prim's algorithm \citep{Prim1957}, 
we find a minimum spanning tree (MST) in the graph,
taking the lengths of the line segments as the weights.
As a results, the line segments corresponding to the edges in the MST
are identified as bridges.
We aggregate the group of original buildings by adding these bridges.

@@

\subsection{Running time}

Although a version with a 
lower running time exists \citep[see][]{Chan1992}, we 
implemented the basic 
version.

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on
C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1. 
The code is available in open source on 
Github\footnote{\url{https://github.com/IGNF/Continuous-Generalisation}}.
The offsetting function and clipping function 
are available from library \textsc{Clipper} of 
\citet{Johnson2014}, which is based on the clipping algorithm of
\citet{Vatti1992Clip}.
The offsetting function is used for the buffering, dilation, 
erosion, and merge operations.
An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
We ran our case study under~64-bit 
Windows~7 on a~$3.3\,$GHz dual core CPU with~$8\,$GB RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
Our testing data is extracted from a dataset produced 
by the French Mapping Agency (IGN);
see \fig\ref{fig:Data}.
The data is at scal~$1:15{,}000$, 
which means~$M_\mathrm{s}=15{,}000$.
It represents the buildings of four towns, 
i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
in the Pyr\'en\'ees-Atlantiques county, south-western France.
IGN also stores a dataset at scale~$1:50{,}000$.
This dataset was basically obtained 
from the data at scale~$1:15{,}000$ 
by buffering with distance~$25\,\mathrm{m}$,
where sometimes distance~$50\,\mathrm{m}$ was also used
in order to identify towns.
A restriction for the town from \citet{Boffet2000} is that 
the longest edge in an MST of the buildings 
should be shorter than~$100\,\mathrm{m}$.

>>>>

A way to achieve continuous generalization is to use morphing.
Often, a start map and a goal map, 
respectively at a larger scale and a smaller scale, 
are used as input, 
then maps at intermediate scales are produced 
while the start map is morphed to the goal map.
In order to morph, correspondences between two maps need to be defined.
For example, corresponding points between a pair of polylines have been 
investigated based on 
dynamic programming \citep{Noellenburg2008}, 
Delaunay triangulations and binary line generalized tree (BLG-tree)  
\citep{Deng2015},
and simulated annealing \citep{Li2017_Annealing}.
From a point to its corresponding point,
a straight-line trajectory is often used to interpolate.
\citet{Peng2013_LSA} defined trajectories based on least-square 
adjustment in order to obtain more reasonable intermediate-scale 
polylines.
Using morphing, \citet{Peng2016_Admin} continuously generalized 
administrative boundaries based on compatible triangulations. 
When the numbers of line features are different 
on the start and goal maps, 
a continuous selection is required and 
\citet{Chimani2014_Eat} proposed to generate a 
selection sequence applicable for road network.
They removed one road at each step while keeping the remaining roads connected.

These methods are interesting but only work on lines and 
our problem of building polygon interpolation 
cannot be achieved by similar morphings. 
Regarding the continuous generalization of polygon features,
\citet{Danciger2009} proposed to grow polygons 
when a map was zoomed out. 
Their method preserves polygons' topology, area-ratios, and 
relative positions.  
In the case where the goal map is an aggregated version of 
start land-cover map, 
\citet{Peng2017_AStar} computed optimal aggregation sequences 
for land-cover areas.

Buildings are important elements on maps, 
many methods have been proposed to generalize them 
but not necessarily in a continuous way.
For example, \citet{haunertwolff2010} simplified a set of 
buildings based an integer program.
Their simplification minimizes the number of edges of 
all the buildings and guarantees that 
the errors are smaller than a user-defined tolerance.
At the same time, no topological conflict 
is introduced by the simplification.
\citet{Buchin2011_Simp} simplified buildings based on 
edge-move operations.
Their method preserves orientations of edges.

When users zoom out on digital maps, 
buildings become smaller and 
the distances between buildings decrease. 
So simplification is not the only necessary operation, 
and buildings can also be 
aggregated to legible enough \cite{Weibel1997}. 
Several methods were proposed 
to aggregate buildings while preserving their shape 
(right angles remain) 
\cite{Regnauld2001,RegnauldRevell07,Damen2008}. 
These algorithms can be used as inspirations 
to define a continuous transformation of buildings.

@@

Finally, some papers directly tackle 
the continuous transformation of buildings 
when scale is reduced. 
\citet{Li2017_Building} morphed between two buildings 
at different scales.
They managed to preserve the orthogonal characteristics of 
buildings, but their algorithm cannot be used in our case 
as our goal map does not contain buildings anymore.
\citet{Touya17b} proposed a progressive transformation of 
buildings into a built-up area, 
where buildings are progressively replaced 
by the shape of the block they belong to. 
However, this last algorithm is not continuous enough, 
as each iteration directly transforms 
a set of buildings in a block into a polygon 
that covers the whole block. 
So there is no existing solution 
for the continuous generalization of building polygons 
into built-up area polygons.

@@

Our way of detecting close buildings is simple.
We buffer buildings with distance $d_{\epsilon, t}/2$ using round joins
(see \fig\ref{fig:Buffer_ThreeKinds}b).
We merge the buffers that overlap each other.
The buildings intersect the same merged buffer 
are identified as a group of close buildings.
The corresponding original buildings 
are identified as a group of original close buildings.
For each pair of the original buildings in the same group,
we connect them by adding a line segment linking the nearest points.
The line segments for a group of original buildings may cross each other or 
even intersect buildings.
To make the topology simple, 
we only select some of the line segments as \emph{bridges}.  
We consider each building as a node and each line segment as an edge, 
then we have a graph.
Using Prim's algorithm \citep{Prim1957}, 
we find a minimum spanning tree (MST) in the graph,
taking the lengths of the line segments as the weights.
As a result, the line segments corresponding to the edges in the 
MST
are identified as bridges.
We aggregate the group of original buildings by adding these bridges.

@@

\subsection{Running time}
Suppose that our input has $n$ edges in total.
Operations like growing, dilation, erosion, merge, and clip 
cost time $O(n^2)$ \citep{Greiner1998Clipping,Palfrader2015}.
Although we iteratively aggregate (see \sect\ref{sec:Aggregate}),
it is unlikely that we need to repeat the aggregation more than 
twice.
Therefore, let us say that the iterative aggregation does not
take extra running time.
Simplifying polygons using Imai--Iri algorithm needs time
$O(n^3)$.
The improved version of Imai--Iri algorithm by 
\citet{Chan1996} does not help in our case
because we have more constraints when simplifying
(see \sect\ref{sec:ImaiIri}).
As a result, the simplification dominates our running time,
which is in $O(n^3)$.

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on
C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1. 
The code is available in open source on 
Github\footnote{\url{https://github.com/IGNF/Continuous-Generalisation}}.
The offsetting function and clipping function 
are available from library \textsc{Clipper} of 
\citet{Johnson2014}, which is based on the clipping algorithm of
\citet{Vatti1992Clip}.
The offsetting function is used for the buffering, dilation, 
erosion, and merge operations.
We ran our case study under~64-bit 
Windows~7 on a~$3.3\,$GHz dual core CPU with~$8\,$GB RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
Our testing data is extracted from a dataset produced 
by the French Mapping Agency (IGN);
see \fig\ref{fig:Data}.
The data is at scal~$1:15{,}000$, 
which means~$M_\mathrm{s}=15{,}000$.
It represents the buildings of four towns, 
i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
in the Pyr\'en\'ees-Atlantiques county, south-western France.
IGN also stores a dataset at scale~$1:50{,}000$.
This dataset was basically obtained 
from the data at scale~$1:15{,}000$ 
by buffering with distance~$25\,\mathrm{m}$,
where sometimes distance~$50\,\mathrm{m}$ was also used
in order to identify towns.
A restriction for the town from \citet{Boffet2000} is that 
the longest edge in an MST of the buildings 
should be shorter than~$100\,\mathrm{m}$.
